---
title: "Example TinyFoxBatt Download"
output: html_document
date: "2024-03-28"
---

# ICARUS TinyFoxBatt Tag prep

Here we provide code to download tag data, do some basic data cleaning steps, and then plot the tracks.

```{r setup, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE}
require(pacman)
p_load(tidyverse,
       mapview)
source("./R/sigfox_download.R")
source("./R/sigfox_to_move2.R")
source("./R/tracking_data_processing.R")
```

# 1. Import your tag data
Provide the tag IDs and all other capture data you have available for your bats.

```{r import_data}
capture_sheet <- data.frame(tag_id = c("120CC52", "120AFC0", "120CCDB"),
                            bat_weight = NA,
                            tag_weight = NA,
                            ring = NA,
                            species = rep("N. noctula", 3))
```


# 2. Download the data
All Sigfox messages should be stored on a database associated with the tag. Here we can include all the fields from the capture sheet to add to our tracks.
```{r download_data}
data <- sigfox_download(tag_ID = capture_sheet$tag_id,
                        species = capture_sheet$species)
```
# Process data 
Here we can do some basic processing and cleaning steps to the data
a. remove locations before deployment
b. format the tracks as a move object
c. calculate basic movement statistics (e.g. ground speed)
d. plot the data in a static map
```{r process_data}
deployment_date <- ymd("2024-03-22")
m <- sigfox_to_move2(data %>% filter(timestamp > deployment_date), motionless = FALSE)
```

# 3. View data on an interactive map
We can take the move2 tracks and plot them on an interactive mapview map. If you click on a point you can then see all sensor and metadata associated with that location.
```{r plot_map}
mapview(m[[1]], zcol = "x24h_active_percent", layer.name = "24hr Activity %", color = heat.colors(8))+
  mapView(m[[2]], layer.name = "Tracks", color = rainbow(10))
```

