---
title: "Example TinyFoxBatt Download"
output: html_document
date: "2024-03-28"
---

# ICARUS TinyFoxBatt Tag prep

Here we provide code to download tag data, do some basic data cleaning steps, and then plot the tracks.

```{r setup, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE}
# devtools::install_github("ehurme/SigfoxTagPrep")
library(SigfoxTagPrep)
# source("R/sigfox_download.R")
# source("R/sigfox_to_move2.R")
# source("R/tracking_data_processing.R")
```

# 1. Import your tag data
Provide the tag IDs and all other capture data you have available for your bats.
```{r import_data, cache = TRUE}
capture_sheet <- data.frame(tag_id = c("9E6FD2", "9E7B0B", "9EAF51", "9ED91A"),
                            time = rep(as.POSIXct("2025-03-17 11:30:00"), 4),
                            attachment_type = rep("Sauer", 4),
                            capture_weight = NA,
                            latitude = rep(2.5, 4), 
                            longtitude = rep(41.6, 4),
                            bat_weight = NA,
                            tag_weight = NA,
                            ring = NA,
                            species = rep("N. leisleri", 4))
```


# 2. Download the data
All Sigfox messages should be stored on a database associated with the tag. Here we can include all the fields from the capture sheet to add to our tracks.
```{r download_data, cache = TRUE}
data <- sigfox_download(tag_ID = capture_sheet$tag_id, 
                        tag_type = "nanofox",
                        release_time = capture_sheet$time,
                        capture_longitude = capture_sheet$longtitude,
                        capture_latitude = capture_sheet$latitude,
                        species = capture_sheet$species)
data$tag_ID %>% table
```
# Process data 
Here we can do some basic processing and cleaning steps to the data
a. remove locations before deployment
b. format the tracks as a move object
c. calculate basic movement statistics (e.g. ground speed)
d. plot the data in a static map
```{r process_data, cache=TRUE}
deployment_date <- ymd("2025-03-17")
Data <- data %>% filter(timestamp > deployment_date)
s <- sigfox_to_move2(Data, motionless = FALSE, make_lines = TRUE)
s
```

# 3. View data on an interactive map
We can take the move2 tracks and plot them on an interactive mapview map. If you click on a point you can then see all sensor and metadata associated with that location.
```{r plot_map}
clean_points <- s[[1]] %>% 
  mt_set_track_id(value = "tag_id") %>%
    mt_set_time(value = "timestamp") %>% 
  filter(!st_is_empty(geometry))

mapview(clean_points, zcol = "tag_id", layer.name = "Tag ID")+
  mapView(s[[2]], zcol = "tag_id", layer.name = "Tracks")
```

```{r}
# ggplot(s[[1]], aes(timestamp, device, size = x24h_active_percent))+geom_point()
ggplot(s[[1]], aes(timestamp, pressure_mbar, col = device))+geom_path()+geom_point()

```

